\documentclass[11pt,letterpaper]{article}
\author{Jann Marc Villablanca}
\title{Resume}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default, scale=0.8]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{fontawesome}
\usepackage{enumitem}
\setlist[itemize]{topsep=0pt, itemsep=0pt, parsep=0pt}
\usepackage{titlesec}
\titlespacing*{\section}
{0pt}{1ex}{1ex}
\titlespacing*{\subsection}
{0pt}{1ex}{1ex}
\titlespacing*{\subsubsection}
{0pt}{1ex}{0pt}

\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

\newenvironment{pipeseparateditemize}[1][]{
    \begin{itemize}[label={}, #1]
        % hacky workaround to make LaTeX compile since {itemize} is expecting an \item
        \item
    \def\separator{}
    \def\item{\ifhmode \unskip\space|\space\fi\relax\ignorespaces\separator}
}{%
    \end{itemize}
}


% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 &
#2 \\
\end{tabular*}}


% Format three pieces of text: left aligned, center aligned, and right aligned
\newcommand{\headerrowthree}[3]{%
  \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
    #1 & % Left aligned
    #2 & % Center aligned
    #3 \\ % Right aligned
  \end{tabular*}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
	{\LARGE \textbf{Jann Marc Villablanca}}\\
	Quezon City, Philippines
	\vspace{0.05cm}
	\\
	\raisebox{-0.2\height}{\Large \faEnvelopeSquare} \ \ jmfv.dev@gmail.com \hfill \raisebox{-0.2\height}{\Large \faGithubSquare} \ \ github.com/jfvillablanca \hfill \raisebox{-0.2\height}{\Large \faLinkedinSquare} \ \ linkedin.com/in/jmfv
\end{center}

\hrule
\section*{\Large Skills}

\begin{pipeseparateditemize}[leftmargin=1em,noitemsep]
    \item Javascript
    \item HTML5
    \item CSS3
    \item Typescript
    \item Node
    \item Express
    \item MongoDB
    \item React
    \item Redux
    \item Linux
    \item Vue
    \item TailwindCSS
    \item Tanstack
    \item Git
    \item CI/CD
    \item Nix/NixOS
    \item Docker
    \item MaterialUI
    \item Jest
    \item Python
    \item Rust
    \item Haskell
    \item Test-Driven Development
    \item Unit Testing
    \item Integration Testing
    \item Frontend
    \item Backend
    \item Full-Stack
\end{pipeseparateditemize}

\section*{\Large Experience}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
	\item
	      \headerrowthree
          {\textbf{\textit{Software Engineer}}}
	      {\textbf{Bridge360 PH}}
	      {\textit{December 2023 - Present}}
	      \begin{itemize*}
            \item \textbf{Reported directly to CEO}: Led the design and implementation of the \textbf{Accounting and Finance modules} within the ADAL Education Management System, enabling secure processing of thousands of \textit{high-volume, ACID-compliant transactions} to ensure data integrity and reliability for critical financial operations.
            \item Developed an internal \textbf{CLI} tool for \textbf{non-technical project managers} to visually test pull requests. Using Nix for \textit{automated setup}, it clones the repo, switches branches, and runs a dev server—\textbf{accelerating development feedback cycle}.
            \item Initiated an \textbf{incremental adoption to Typescript} for our Web and API service codebases by using scripts to automate the migration.
            \item Enhanced \textbf{developer experience} by implementing \textbf{Git hooks} for automated linting and formatting pre-pull request, \textit{significantly reducing code review time} and improving code quality.
            \item Boosted \textbf{API performance} by over \textit{80\%} on high-traffic search queries through \textit{server-side pagination}, reducing payload size and latency for faster, scalable responses.
            \item Mentored junior developers in effective \textbf{Git workflows}, concise commit messages, and both stack-specific and software engineering best practices, reducing code review cycles by \textit{30\%} and enhancing codebase maintainability.
            \item Performed in-depth \textbf{code reviews} on pull requests, enforcing best practices and reducing post-release bugs by \textit{25\%}.
            \item Designed and developed a \textbf{Point of Sale (POS) system} within the ADAL EMS platform, supporting multi-concessionaire transaction processing and inventory management.
            \item Streamlined local development by setting up a \textbf{Nix-based environment} with self-managed \textbf{MongoDB} replica sets, enabling developers to spin up sandboxed instances and freely test database changes with automated dump and restore commands.
	      \end{itemize*}
	      	      
  \subsubsection*{\large Open Source Software Contributor}
	\item
	      \headerrowthree
          {\textbf{\textit{Nixpkgs maintainer}}}
	      {github.com/\textbf{NixOS/nixpkgs}}
	      {\textit{April 2023 - Present}}
          {\emph{\textbf{nixpkgs} is the largest and the most-up-to-date package repository for Unix-based systems}}
 
	      \begin{itemize*}
            \item Contribute to the maintenance of various software packages in the repository, ensuring \textit{up-to-date} and \textit{reliable releases}.
            \item Package a diverse range of open-source projects, including \textit{Rust applications}, \textit{Python libraries}, and \textit{Vim plugins}, enhancing the ecosystem for developers.
	      \end{itemize*}

	\item
	      \headerrowthree
          {\textbf{\textit{Core maintainer}}}
	      {github.com/\textbf{neon-mmd/websurfx}}
	      {\textit{December 2023 - Present}}
          {\emph{\textbf{websurfx} is a modern, lightning-fast, privacy-oriented, and secure meta search engine written in Rust.}}

	      \begin{itemize*}
            \item Integrated two search engines, \textit{Mojeek} and \textit{Bing}, expanding the search result pool and significantly enhancing the breadth of aggregated content.
            \item Actively maintain the project’s \textit{flake.nix} to ensure seamless builds and improve documentation for developers relying on the Nix dev shell.
            \item Supplemented the project by adding support for parsing \textbf{JSON} responses from upstream search engines, streamlining data aggregation and improving efficiency alongside existing \textbf{web scraping} methods.
	      \end{itemize*}
	      	      
\subsubsection*{\large Previous Professional Experience}
	\item
	      \headerrowthree
	      {\emph{Warehouse Operations Engineer}}
	      {\textbf{Striga Bikes Enterprises}}
	      {\textit{May 2020 - September 2022}}
	      \begin{itemize*}
            \item Led transition from in-store bike sales to a high-volume e-commerce and B2B fulfillment model.
	      \end{itemize*}
	      	      
	\item
	      \headerrowthree
	      {\emph{Science Research Specialist}}
	      {\textbf{DOST - Philippine Nuclear Research Institute}}
	      {\textit{January 2019 - February 2020}}
	      \begin{itemize*}
            \item Directed the design and development of a Cesium-137 source in-situ calibration system for monitoring stations.
	      \end{itemize*}
\end{itemize}

\section*{\Large Education}

\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
	\item
	      \headerrow
	      {\textbf{University of the Philippines - Diliman}}
	      {\textbf{Quezon City, Philippines}}
	      \headerrow
	      {\emph{B.S. Electronics and Communications Engineering}}
	      {\emph{June 2013 -- December 2018}}
	      	      
\end{itemize}

\end{document}
